---
title: "Machine Learing"
author: "Karin"
date: "3 Mai 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R data structures
The most typical structures used in machine learning are **vectors**, **factors**, **lists**, **arrays**, and **data frames**.

### Vector
Vectors stores an ordered set of values called elements. A vector can contain any number of element however they need to be the same type. So a vector type cannot be nummerical and categorical at the same time.

There are several vector types commonly used: *integer* (numbers without decimals), *numeric* (numbers with decimals), *character* (text), or *logical* (TRUE or FALSE values). There are also two special values: *NULL*, which is used to indicate the absence of any value, and *NA*, which indicates a missing value.

### Factors
A factor is a special case of vector that is solely used for representing nominal variables or categorical variable. Change character vector so you can use it for algorithms and also can save memory. In R you apply factor() function 
```{r }
gender <- factor(c("MALE", "FEMALE", "MALE"))
gender
```

```{r}
library(RWeka) # functions to the machine learning algorithms by Ian H. Witten and Eibe Frank
library(tidyverse)
li
```

## Including Plots
```{r }

```

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
